\section{Preliminaries}
\label{sec:prelim}

\subsection{Markov Decision Processes and Offline RL} 

We study RL in the framework of Markov decision processes (MDPs) specified by the tuple $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \transitions, r, \mu_0, \gamma)$.
$\mathcal{S}, \mathcal{A}$ denote the state and action spaces. 
$\transitions(\bs' | \bs, \ba)$ and $r(\bs,\ba) \in [-R_{\max}, R_{\max}]$ represent the dynamics and reward function respectively. 
$\mu_0(s)$ denotes the initial state distribution, and $\gamma \in (0,1)$ denotes the discount factor. 
We denote the discounted state visitation distribution of a policy $\pi$ using \hbox{$d_\mathcal{M}^\pi(\bs) := (1 - \gamma)\sum_{t=0}^\infty\gamma^t\mathcal{P}(s_t = \bs | \pi)$}, where $\mathcal{P}(s_t = \bs | \pi)$ is the probability of reaching state $\bs$ at time $t$ by rolling out $\pi$ in $\mathcal{M}$. Similarly, we denote the state-action visitation distribution with $d_\mathcal{M}^\pi(\bs, \ba) \coloneqq d_\mathcal{M}^\pi(\bs)\pi(\ba|\bs)$. The goal of RL is to learn a policy that maximizes the return, or long term cumulative rewards:
\begin{equation}
    \max_\policy J(\mathcal{M}, \policy) := \frac{1}{1-\gamma}\E_{(\bs, \ba) \sim d_\mathcal{M}^\pi(\bs, \ba)}[r(\bs, \ba)].
\end{equation}


Offline RL is the setting where we have access only to a fixed dataset $\mathcal{D} = \{(\bs, \ba, r, \bs')\}$, which consists of transition tuples from trajectories collected using a behavior policy $\behavior$. In other words, the dataset $\mathcal{D}$ is sampled from $d^\behavior(\bs, \ba) \coloneqq d^\behavior(\bs) \behavior(\ba|\bs)$. We define $\mdpbar$ as the empirical MDP induced by the dataset $\mathcal{D}$ and $d(\bs,\ba)$ as sampled-based version of $d^\behavior(\bs, \ba)$. In the offline setting, even in the limit of an infinite size dataset, it may not be possible to find the optimal policy for the underlying MDP~\cite{Chen2019InformationTheoreticCI, kidambi2020morel}.
Thus, we typically forgo the goal of finding the optimal policy, and instead aim to find the best possible policy using the fixed offline dataset.

\subsection{Model-Free Offline RL Algorithms}
\label{sec:conservative_model_free}
One class of approaches for solving MDPs involves the use of dynamic programming and actor-critic schemes~\cite{SuttonBook, BertsekasBook}, which do not explicitly require the learning of a dynamics model. To capture the long term behavior of a policy without a model, we define the action value function as
\begin{align}
    Q^\pi(\bs, \ba) & := \mathbb{E} \left[ \sum_{t=0}^\infty \gamma^t \ r(\bs_t, \ba_t) \mid \bs_0 = \bs, \ba_0 = \ba \right], % \\
    % V^\pi(\bs) & := \mathbb{E} \left[ \sum_{t=0}^\infty \gamma^t \ r(\bs_t, \ba_t) \mid \bs_0 = \bs \right]
\end{align}
where future actions are sampled from $\policy(\cdot|\bs)$ and state transitions happen according to the MDP dynamics. Consider the following Bellman operator:
\[
\mathcal{B}^\policy Q (\bs, \ba) := r(\bs, \ba) + \gamma \mathbb{E}_{\ \bs' \sim \transitions(\cdot | \bs, \ba), \ba' \sim \policy(\cdot | \bs')} \left[ Q(\bs', \ba') \right],
\]
and its sample based counterpart:
\[
\widehat{\mathcal{B}}^\policy Q (\bs, \ba) := r(\bs, \ba) + \gamma Q(\bs', \ba'),
\]
associated with a single transition $(\bs, \ba, \bs')$ and $\ba' \sim \policy (\cdot | \bs')$. The action-value function satisfies the Bellman consistency criterion given by $\mathcal{B}^\policy Q^\policy(\bs, \ba) = Q^\policy (\bs, \ba) \ \forall (\bs, \ba)$. When given an offline dataset $\mathcal{D}$, standard approximate dynamic programming~(ADP) and actor-critic methods use this criterion to alternate between policy evaluation~\cite{Munos2008FiniteTimeBF} and policy improvement. A number of prior works have observed that such a direct extension of ADP and actor-critic schemes to offline RL leads to poor results due to distribution shift over the course of learning and over-estimation bias in the $Q$ function~\cite{fujimoto2018off, kumar2019stabilizing, wu2019behavior}. To address these drawbacks, prior works have proposed a number of modifications aimed towards regularizing the policy or value function (see Section~\ref{sec:related}). In this work, we primarily focus on CQL~\cite{kumar2020conservative}, which alternates between the two following steps.

{\bf Policy Evaluation:} The $Q$ function associated with the current policy $\policy$ is approximated conservatively by repeating the following optimization:

\vspace*{-15pt}
\begin{small}
\begin{align}
    {Q}^{k+1} \leftarrow& \arg\min_{Q} \beta\left(\E_{\bs \sim \mathcal{D}, \ba \sim \mu(\cdot|\bs)}\left[Q(\bs,\ba)\right]- \E_{\bs, \ba \sim \mathcal{D}}\left[Q(\bs,\ba)\right]\right)\nonumber\\
    +& \frac{1}{2}\E_{\bs, \ba, \bs' \sim \mathcal{D}}\left[ \left(Q(\bs, \ba) - \widehat{\bellman}^\policy {Q}^k(\bs, \ba))\right)^2 \right],
    \label{eq:cql_loss}
\end{align}
\end{small}
\vspace*{-15pt}

where $\mu(\cdot|s)$ is a wide sampling distribution such as the uniform distribution over action bounds. CQL effectively penalizes the $Q$ function at states in the dataset for actions not observed in the dataset. This enables a conservative estimation of the value function for any policy~\cite{kumar2020conservative}, mitigating the challenges of over-estimation bias and distribution shift.

{\bf Policy Improvement:} After approximating the Q function as $\hat{Q}^\policy$, the policy is improved as
\[
\policy \leftarrow \arg \max_{\policy'} \ \mathbb{E}_{\bs \sim \mathcal{D}, \ba \sim \policy'(\cdot | \bs)} \left[ \hat{Q}^\policy (\bs, \ba) \right].
\]
Actor-critic schemes with parameterized policies and $Q$ functions approximate the $\arg \max$ and $\arg \min$ in above equations with a few steps of gradient descent.

%%AK.3.2: define the empirical MDP here...

\subsection{Model-Based Offline RL Algorithms}
\label{sec:prelim_offline_mbrl}
A second class of algorithms for solving MDPs involve the learning of the dynamics function, and using the learned model to aid policy search. Using the given dataset $\mathcal{D}$, a dynamics model $\widehat{T}$ is typically trained using maximum likelihood estimation as:
$\min_{\widehat{T}} \ \mathbb{E}_{(\bs, \ba, \bs') \sim \mathcal{D}} \left[ \log \widehat{T}(\bs' | \bs, \ba) \right]$.
A reward model $\hat{r}(\bs, \ba)$ can also be learned similarly if it is unknown. Once a model has been learned, we can construct the learned MDP $\widehat{\mathcal{M}} = (\mathcal{S}, \mathcal{A}, \widehat{T}, \hat{r}, \mu_0, \gamma)$, which has the same state and action spaces, but uses the learned dynamics and reward function. 
%Subsequently, any policy learning~\cite{schulman2017proximal, haarnoja2018soft, Abdolmaleki2018MaximumAP, Rajeswaran-Game-MBRL} or planning algorithm~\cite{Todorov2005, WilliamsMPPI, POLO, Nagabandi2019DeepDM} can be used to recover the optimal policy in the model as $\hat{\policy} = \arg \max_{\policy} J(\widehat{\mathcal{M}}, \policy).$
Subsequently, any policy learning or planning algorithm can be used to recover the optimal policy in the model as $\hat{\policy} = \arg \max_{\policy} J(\widehat{\mathcal{M}}, \policy).$
%%AR: Removing citations here to save space. Cover them in related works!

This straightforward approach is known to fail in the offline RL setting, both in theory and practice, due to distribution shift and model-bias~\cite{RossB12, kidambi2020morel}. In order to overcome these challenges, offline model-based algorithms like MOReL~\cite{kidambi2020morel} and MOPO~\cite{yu2020mopo} use uncertainty quantification to construct a lower bound for policy performance and optimize this lower bound. By using an uncertainty estimation algorithm like bootstrap ensembles~\cite{OsbandAC18, Azizzadenesheli18, POLO}, we can obtain $u(\bs, \ba)$, an estimate of uncertainty in dynamics model prediction. In the case of MOPO, an uncertainty penalized MDP is constructed where the reward is given by
$\widetilde{r} (\bs, \ba) = \hat{r}(\bs, \ba) - \lambda u(\bs, \ba)$,
and the learned dynamics model is used without modification. MOPO learns a policy in this ``uncertainty-penalized'' MDP $\widetilde{\mathcal{M}} = (\mathcal{S}, \mathcal{A}, \widehat{T}, \widetilde{r}, \mu_0, \gamma)$ which has the property that $J(\widetilde{\mathcal{M}}, \policy) \leq J(\mathcal{M}, \policy) \ \forall \policy$. 
%%TY.2.1: We should probably make the notations on different MDPs consistent. In the theory section, we use \widetilde{\mathcal{M}} for the learned MDP and \widehat{M} for the empirical MDP.
By constructing and optimizing such a lower bound, offline model-based RL algorithms avoid the aforementioned pitfalls like model-bias and distribution shift.
While any RL or planning algorithm can be used to learn the optimal policy for $\widetilde{\mathcal{M}}$, we focus specifically on MBPO~\cite{janner2019trust, sutton1991dyna} which was used in MOPO. MBPO follows the standard structure of actor-critic algorithms, but in each iteration uses an augmented dataset $\data \cup \data_{\text{model}}$ for policy evaluation. Here, $\data$ is the offline dataset and $\data_{\text{model}}$ is a dataset obtained by simulating the current policy using the learned dynamics model. 
Specifically, at each iteration, MBPO performs $k$-step rollouts using $\widehat{T}$ starting from state $\bs \in \mathcal{D}$ with a particular rollout policy $\mu(\ba|\bs)$, adds the model-generated data to $\data_{\text{model}}$, and optimizes the policy with a batch of data sampled from $\mathcal{D} \cup \data_{\text{model}}$ where each datapoint in the batch is drawn from $\mathcal{D}$ with probability $f \in [0, 1]$ and $\data_{\text{model}}$ with probability $1 - f$.
%%AR: The above goes into too many details. Shortening it a bit to highlight the important points.


% Using this, in the case of MOReL~\cite{kidambi2020morel} a pessimistic MDP is formed using the dynamics $\widetilde{T}(\cdot|\bs, \ba) = \delta(HALT)$ if $u(\bs, \ba) \geq \alpha$ and $\widetilde{T}(\cdot|\bs, \ba) = \widehat{T}(\cdot | \bs, \ba)$ otherwise; $\widetilde{r}(\bs, \ba) = -R_\max$ if $u(\bs, \ba) \geq \alpha$ and $\widetilde{r}(\bs, \ba) = \hat{r}(\bs, \ba)$ otherwise. In the case of MOPO, 

%%SL.1.31: Assuming this is a stub that will be filled in later?
%%AR: Yes, was going to write it now.