% First and foremost, I am tremendously grateful for my adviser Sergey Levine for his continuous support and guidance throughout my PhD. Besides heavily influecing my technical growth, Sergey provided me with the the freedom to work on problems of my interest, allowing me to pursue probe-driven research, and has taught me the art of asking the right questions, whose importance I now realize. I am also grateful to Sergey for teaching me how to think about the big picture questions. I am also very grateful to George Tucker, who has been a long-term collaborator of mine, starting from the second paper I wrote in my PhD. Most notably, I have learned from him the importance of critical examination of research ideas. Thank you my quals and dissertation committee members Jiantao Jiao, Emma Brunskill, and Jennifer Listgarten for your support, guidance, and fruitful conversations. I am also grateful to Geoffrey Hinton for taking a chance on me when I did not know much about machine learning and hosting me as an intern at Google Brain Toronto in 2017, and for introducing me to reinforcement learning, which is the area I studied for my Ph.D. 

% I have had the great fortune to be able to collaborate with a number of faculty members, students, post-doctoral scholars, and researchers throughout my Ph.D. In the initial years of my PhD, I started exploring the topic of offline RL with Justin Fu. At the time, I also worked with Abhishek Gupta on several topics aimed to understand temporal-difference learning. These were both immense learning experiences for me. I also learned a lot pertaining to implementation of a variety of RL algorithms working with Jason Peng. I am grateful to have had the opportunity to work with these senior graduate student collaborators in the initial years of my PhD. Since the middle of my PhD, I have collaborated extensively with and learned a lot from Chelsea Finn, Tianhe Yu, Rishabh Agarwal, Anikait Singh, Young Geng, Frederik Ebert, Dibya Ghosh, Yi Su, Amir Yazdanbakhsh, Avi Singh, Colin Li, and Quan Vuong. In particular, I would like to thank Rishabh Agarwal and Tianhe Yu, together with whom I explored several new research topics. I would also like to thank Rishabh Agarwal for teaching me how to systematically organize experiments and compile results. I thank Young Geng for answering countless queries about Jax, helping me with implementation, and asking hard questions on projects I pursued and my research ideas that enabled me to grow as a researcher. I am also grateful to all other collaborators I ahve worked with: Saurabh Kumar, <FINSH> I would also especially like to thank all undergraduate and master's students I worked with: Brandon Trabucco, Anikait Singh, Kevin Li, Ria Doshi, Homanga Bharadhwaj, Rafael Rafailov, Han Qi, Chet Bhateja, Derek Guo, and Jason Wang for their hardwork and dedication on the projects.      

% During my PhD, I was a part-time student researcher at Google Brain from 2020-2023. I was hosted by George Tucker and Amir Yazdanbakhsh, two excellent mentors, who gave me the freedom to work on any topic I wanted and collaborate with anyone. I am grateful to all researchers and engineers I have talked to and collaborated with at Google in this time, including those that never made it into a publication or release, but gave me a lot of perspective about problems. Thank you Sandra Faust, Dale Schuurmans, Minmin Chen, Yevgen Chebotar, John Sipple, and Ofir Nachum, for sharing your perspectives and thoughtful conversations.   

% I would also like to thank members of the RAIL lab and the broader BAIR community for a supportive and friendly atmosphere in the lab. Thanks to the open layout of the lab, I enjoyed random conversations on BWW8. I also enjoyed the late nights near paper deadlines. Special thanks to Young Geng and Michael Janner, graduate students in RAIL in my cohort: our high-level philosophical discussions about research trends over coffee and food have greatly shaped my thoughts. The middle years of my PhD were in the height of the COVID pandemic and hence remote, but I greatly enjoyed discussing with and learned a lot from the members of RAIL before and after. Thank you Abhishek, Frederik, Justin, Michael, Aurick, Kelvin, Nick, Rowan, Natasha, Dhruv, Manan, Dibya, Colin, Laura, Katie, Marwa, Mitsuhiko, Simon, Oleh, Karl, Homer, Kevin, Kuan, and others, for making my PhD years fun, both research and other-wise. 

% My experience during graduate school has been made ever so enjoyable by my amazing group of friends, both in Berkeley and outside. Thank you Karan, Siddharth, Shubham, Anurag, and Manan, for supporting and helping me when I needed it the most. Thank you Saurabh, Siddhant, Sumith, Utkarsha, and Amrith for providing me advice at various points during these years. My time at Berkeley would not have been the same without the coffee from Blue Bottle and tea from Asha's, the deadline food from the Noodle, Bangkok Thai, Bongo Burger, and Urban Turbann (Now called Xpressions), as well as 6 am paper deadline breakfasts from Noah's Bagels and McDonalds.  

% Finally, I would like to thank my parents, Mukesh Saxena and Sadhna Sinha: thank you for giving me the freedom to pursue my dreams, teaching me the immense value of helping others, and never letting me feel alone 8000 miles away.

First and foremost, I am tremendously grateful to my adviser, Sergey Levine, for his continuous support and guidance throughout my Ph.D. Besides heavily influencing my technical growth and a lot of ideas in this dissertation, Sergey provided me with the freedom to work on problems of my interest, allowing me to pursue research that I wanted, and has taught me the art of asking the right questions, the importance of which I now realize. I am also grateful to Sergey for teaching me how to think about the big-picture questions. He is the smartest researcher I have met so far and I believe I could not have had a better advisor.

I am very grateful to George Tucker, who has been a long-term collaborator of mine since my second paper in my Ph.D. Most notably, I have learned from him the importance of critical examination of research ideas. George's critical questions have always made me and my work better and I really appreciate him for this. Thank you to my qualifying examination and dissertation committee members Jiantao Jiao, Emma Brunskill, and Jennifer Listgarten for your support, guidance, and fruitful discussions. I am also extremely grateful to Geoffrey Hinton for taking a chance on me when I did not know much about machine learning and hosting me as an intern at Google Brain Toronto in 2017, and for introducing me to reinforcement learning, which is the area I studied for my Ph.D. I am also very thankful to Pieter Abbeel for his advice on research and career at multiple points during my Ph.D., most notably during the first year of my PhD.  

I have had the great fortune to collaborate with a number of faculty members, students, post-doctoral scholars, and researchers throughout my Ph.D. In the initial years of my Ph.D., I started exploring the topic of offline RL with Justin Fu. At the time, I also worked with Abhishek Gupta on several topics aimed at understanding temporal-difference learning. These were both immense learning experiences for me. I also learned a lot pertaining to the implementation of a variety of RL algorithms while working with Jason Peng. I am grateful to have had the opportunity to work with these senior graduate student collaborators in the initial years of my Ph.D. 

Since the middle of my Ph.D., I have collaborated with and learned a lot from Chelsea Finn, Tianhe Yu, Rishabh Agarwal, Young Geng, Anikait Singh, Amir Yazdanbakhsh, Abhishek Gupta, Dibya Ghosh, Yi Su, Avi Singh, Frederik Ebert, Colin Li, and Quan Vuong. In particular, I would like to thank Rishabh Agarwal and Tianhe Yu, with whom I explored several new research topics that established a line of work covered in this thesis. I would like to thank Rishabh Agarwal for teaching me how to systematically organize experiments and compile results, a skill that will be very valuable for my future. I would like to thank Young Geng for answering countless queries about Jax, being my go-to person to ask for implementation advice, and asking hard questions on projects I pursued and my research ideas that enabled me to grow as a researcher. I am also grateful to all other collaborators I have worked with: Yi Su, Mitsuhiko Nakamoto, Saurabh Kumar, Simon Zhai, Anurag Ajay, Aurick Zhou, Joey Hong, Tengyu Ma, Karol Hausman, Yevgen Chebotar, Zhang-Wei Hong, Manan Tomar, Katie Kang, Kuba Grudzien, Nick Rhinehart, Rafael Rafailov, Amy Lu, Ofir Nachum, Aravind Rajeswaran, Homer Walke, Florian Shkurti, Animesh Garg, Nilah Ionidis, Grace Gu, Zico Kolter, Priya Donti, Melrose Roderick, and Pulkit Agarwal. I would also especially like to thank all undergraduate and master's students I worked with: Brandon Trabucco, Anikait Singh, Kevin Li, Yanlai Yang, Sathvik Kolli, Homanga Bharadhwaj, Jonathan Yang, Albert Yu, Stephen Tian, Han Qi, Ria Doshi, Chet Bhateja, Derek Guo, and Jason Wang for their hard work and dedication to the projects. These students are now leaders in emerging areas of AI and I eagerly look forward to their future successes.

During my Ph.D., I was a part-time student researcher at Google Brain from 2020 to 2023. I was hosted by George Tucker and Amir Yazdanbakhsh, two excellent mentors, who gave me the freedom to work on any topic I wanted and collaborate with anyone. I started to appreciate the importance of looking at applied problems and learned a lot about systems working with Amir. Amir would never turn my silly questions time and always make time to discuss with me, which I am very thankful about. I am grateful to all researchers and engineers I have talked to and collaborated with at Google during this time. Many times a lot of these discussions and collaborations never made it into a publication or release, but gave me a lot of perspective about real-world problems. Thank you, Sandra Faust, Dale Schuurmans, Minmin Chen, Marc Bellemare, Yevgen Chebotar, Karol Hausman, Hossein Mobahi, Kevin Swersky, Mohammad Norouzi, Yundi Qian, John Sipple, Sherry Yang, Yingjie Miao, Jordi Orbay, and Ofir Nachum, for sharing your perspectives and thoughtful conversations.

I would also like to thank the members of the RAIL lab and the broader BAIR community for creating a supportive and friendly atmosphere in the lab. Thanks to the open layout of the lab, I enjoyed engaging in several conversations on BWW8, that would start randomly over lunch, coffee, or near the desk area. Special thanks to Young Geng and Michael Janner, graduate students in RAIL in my cohort: our high-level philosophical discussions about research trends over coffee and food have greatly shaped my thoughts. The middle years of my Ph.D. were during the height of the COVID pandemic and hence, a time when we were all remote, but I greatly enjoyed hanging out with and learned a lot from the members of RAIL before and after. Thank you, Michael Janner, Abhishek, Frederik, Justin, Michael Chang, Aurick, Kelvin, Nick, Rowan, Natasha, Dhruv, Manan, Dibya, Colin, Laura, Katie, Marwa, Amy Lu, Mitsuhiko, Simon, Oleh, Karl, Homer, Kuba, Kevin, Kuan, Amy Zhang, Natasha, Seohong, Kyle, Kristian, Vivek, Philip Ball, Glen, Anusha, Coline, Greg, Dinesh, Vitchyr, JD, Jason, Sid, Avi, Ashvin, Alex Lee, Erin, Marvin, Joey, Charlie, Tuomas, Kate, Jedrzej, and others, for making my Ph.D. years exciting, both research and otherwise. I especially cherish my experiences with hiking ``buddies'' in RAIL including Manan, Colin, and Young, who over a period of 2 months made me realize how beautiful Berkeley hills are and transformed me from someone who would not at all want to walk up Hearst to someone who loves to go up to the peaks in Berkeley hills everyday. I also am grateful to all dinner conversations I have had with Young, Oleh, Karl, and Mitsuhiko, all of which have only made me a better person. Also big thanks to lab members nearby: Young Geng, Marwa Abdulhai, Laura Smith, Rowan McAllister, Amy Zhang, Abhishek Gupta, and Marvin Zhang, for making it fun to be in the lab.

My experience during graduate school has been made ever so enjoyable by my amazing group of friends outside work, both in Berkeley and elsewhere. Thank you, Karan, Siddharth, Shubham, Anurag, and Manan, for being extraordinary roommates and for supporting and helping me selflessly whenever I asked. Thank you, Saurabh, Siddhant, Sumith, Amrith, Utkarsha, Moraldeep, and Upadhi, for providing me fundae at various points during my PhD years. I want to thank Jean Nguyen, Angie Abbatecola, and the rest of the BAIR admin team for their help in making my Ph.D. experience smooth and enjoyable. My time at Berkeley would also not have been the same without the coffee from Blue Bottle and tea from Asha's, the deadline food from the Noodle, Bangkok Thai, Mad Seoul, Bongo Burger, and Urban Turbann, as well as 6 am paper deadline breakfasts from Noah's Bagels and McDonald's.

Finally, I would like to thank my parents, Mukesh Saxena and Sadhna Sinha: thank you for giving me the freedom to pursue my dreams, keeping me sane in times of stress, and never letting me feel alone from the other side of the planet.